\documentclass{article}
\usepackage[utf8]{inputenc}

\title{How to \LaTeX}
\author{Elias Jaffe}
\date{\today}

\usepackage{natbib}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{xspace}

\newcommand{\latex}{\LaTeX \xspace}


\begin{document}

\maketitle

\section{The Basics}
Time to get groovin'.
\begin{itemize}
    \item \latex introduction (start here!) \href{https://www.overleaf.com/learn/latex/Free_online_introduction_to_LaTeX_(part_1)}{Link: \latex Introduction from Overleaf}
    \item Where to \latex? In my experience, Overleaf (free, online) and TexMaker (free, offline/Windows) are my favorites, but here's a massive list. \href{https://tex.stackexchange.com/questions/339/latex-editors-ides}{Link: Stackexchange \latex editors list}
    \item It's dangerous to go alone. Take this! It's my favorite \latex cheatsheet in PDF form. \href{https://www.nyu.edu/projects/beber/files/Chang_LaTeX_sheet.pdf}{Link: \LaTeX 2e cheat sheet from NYU}
    \item Need a symbol and can't find it? Try using handwriting recognition. \href{https://detexify.kirelabs.org/classify.html}{Link: Detexify, Kire Labs}
    \item The unofficial \latex 2e manual. For reference only, not required reading. \href{http://texdoc.net/texmf-dist/doc/latex/latex2e-help-texinfo/latex2e.pdf}{Link: Unofficial \LaTeX 2e manual PDF}
    \item The "not so short" \latex manual. Suggested reading. Est. 2hrs. \href{http://ctan.mirrors.hoobly.com/info/lshort/english/lshort.pdf}{Link: The Not So Short Guide To \LaTeX 2e PDF}
    \item Good (but small) list of math symbols for \latex. \href{https://www.caam.rice.edu/~heinken/latex/symbols.pdf}{Link: Rice.edu list of useful \latex math symbols PDF}
\end{itemize}

\section{Typical Document Features}
\begin{itemize}
    \item Guide to using \latex environments. \href{https://www.overleaf.com/learn/latex/Environments}{Link: Overleaf Environments Article}
    \item \latex table creator. It's very annoying to type tables and matrices by hand. Use this. \href{https://www.tablesgenerator.com/}{Link: Tablesgenerator.com \latex table generator}
    \item How to insert figures and images into your document. \href{https://www.overleaf.com/learn/latex/Inserting_Images}{Link: Overleaf figures article}
    \item PDF links make every document look super tech-savvy. \href{https://www.latex-tutorial.com/tutorials/hyperlinks/}{latex-tutorial.com's guide to clickable links in LaTeX}
    \item Bibliography and references. \href{https://www.overleaf.com/learn/latex/bibliography_management_with_bibtex}{Link: Overleaf bibliography article}
\end{itemize}

\section{Stuff That Makes \latex Superior To Word}
\begin{itemize}
    \item The math typesetting.
    \item Advanced \latex tricks for super amazing documents. \href{https://www.brown.edu/academics/science-center/sites/brown.edu.academics.science-center/files/uploads/advancedLaTeX_0.pdf}{Link: Brown.edu Advanced Latex PDF}
    \item The AMSMath package is super useful. Here's the manual. \href{http://mirrors.rit.edu/CTAN/macros/latex/required/amsmath/amsldoc.pdf}{Link: AMSMath manual PDF}
    \item Very specific spacing in math. \href{https://www.overleaf.com/learn/latex/Spacing_in_math_mode}{Link: Overleaf article on spacing symbols}
    \item PSTricks for advanced plotting and diagrams. Very time consuming, but worthwhile. \href{https://tug.org/PSTricks/main.cgi/}{Link 1: tug.org PSTricks homepage, with loads of breathtaking examples.} \href{https://en.wikibooks.org/wiki/LaTeX/PSTricks}{Link 2: \latex wikibooks PSTricks wiki page, with basic commands.}
    \item Downloading extra packages from CTAN on a local device for extended functionality. \href{http://latex.silmaril.ie/formattinginformation/pkginst.html}{Link: latex.simaril.ie CTAN tutorial}
    \item All the CTAN packages and what they can do. Click the letters up top and browse for a bit. \href{https://ctan.org/pkg/}{Link: CTAN packages}
    
\end{itemize}

\section{Easter Eggs}
\begin{itemize}
    \item The halloweenmath package lets you put ghost, pumpkin, and witch symbols in your math. The application of such a package is obvious, and left as an exercise to the reader. \href{http://ftp.math.purdue.edu/mirrors/ctan.org/macros/latex/contrib/halloweenmath/halloweenmath-man.pdf}{Link: The halloweenmath package manual PDF}
    \item Finally, automatic coffee stains for math papers! \href{http://hanno-rein.de/archives/349}{Hanno-rein.de (the creator's site) on the coffee stain package, with example PDF}
    \item List of fun packages. \href{https://tex.stackexchange.com/questions/67656/are-there-other-fun-packages-like-the-coffee-stains-package}{Link: Stackexchange user compiled list of fun packages}
    \item \latex tricks. \href{http://static.latexstudio.net/wp-content/uploads/2015/01/LaTeX-Tricks-X.pdf}{Link: latexstudio.net misunderstood or underused \latex tricks.}
    \item The comprehensive \latex symbol list contains some cool stuff. \href{http://ctan.math.utah.edu/ctan/tex-archive/info/symbols/comprehensive/symbols-a4.pdf}{Link: CTAN hosted PDF of all \latex symbols.}
\end{itemize}
\end{document}
